\begin{enumerate}[label=\thechapter.\arabic*,ref=\thechapter.\theenumi]

\item In a potato race, a bucket is placed at the starting point, which is 5 m from the first potato,and the other potatoes are placed 3 m apart in a straight line. There are ten potatoes in the line. A competitor starts from the bucket, picks up the nearest potato, runs back with it, drops it in the bucket, runs back to pick up the next potato, runs to the bucket to drop it in, and she continues in the same way until all the potatoes are in the bucket. What is the total distance the competitor has to run?\\
\hfill(NCERT-Maths 10.5.3.20Q)\\
\solution 
\input{ncert-maths/10/5/3/20/main.tex}
\pagebreak

\item Find the sum of the first $15$ multiples of $8$. \\

\solution
\input{ncert-maths/10/5/3/13/assignment12.tex}
ss\pagebreak

\item If the sum of $n$ terms of an A.P. is $3n^2+5n$ and its $m^{th}$ term is 164, find the value of $m$.\\
\solution
\input{ncert-maths/11/9/2/13/main.tex}

\pagebreak
\item Find the sums given below:
\begin{enumerate}
    \item  $7 + \frac{21}{2} + 14 ... + 84$
    \item  $34 + 32 + 30 ... + 10$
    \item  $-5 + -8 + -11 ... -230$
\end{enumerate}
\solution
\input{ncert-maths/10/5/3/2/a1.tex}
\pagebreak
\item Show that $a_0$ , $a_1$ , $a_2$
, . . ., $a_n$
, . . . form an AP where an is defined as below :
\begin{enumerate}
    \item $a_n$ = $(3 + 4n)$ 
    \item $a_n$ = $(9 - 5n)$ 
\end{enumerate}
Also find the sum of the first 15 terms in each case.
\solution
\input{ncert-maths/10/5/3/10/math.10.5.3.10.tex}

\pagebreak
\item If the sum of $n$ terms of an AP is $(pn + qn^2)$, where $p$ and $q$ are constants, find the common difference.
\solution
		\input{ncert-maths/11/9/2/8/Math_11_9_2_8.tex}

\pagebreak
\item Find the sum of the first 40 positive integers divisible by 6\\
	\solution
		\input{ncert-maths/10/5/3/12/main.tex}
\pagebreak
\item If the sum of certain number of terms in a AP 25,22,19,... is 116. Find the last term.\\
\solution
\input{ncert-maths/11/9/2/6/2.tex}
\pagebreak

\item The first and the last terms of an AP are 17 and 350 respectively. If the common difference
is 9, how many terms are there and what is their sum?\\
\solution 
\input{ncert-maths/10/5/3/6/10.5.3.tex}
\pagebreak
\item A small terrace at a football ground comprises of 15 steps each of which is 50
m long and built of solid concrete.Each step has a rise of 1/4 m and a tread of
1/2 m. Calculate the total volume of concrete required to build the terrace.
[Hint: Volume of concrete required to build the first step=\begin{align}
    V&=\frac{1}{4} \cdot \frac{1}{2} \cdot 50 
\end{align}\\
\solution 
\input{ncert-maths/10/5/4/5/assign1.tex}
\pagebreak

\item Given a GP with a = 729 and $7^{th}$ term 64, find $S_7$.\\
\solution 
\input{ncert-maths/11/9/3/15/ncert_11_9_3_15.tex}
\pagebreak

\item Find the sum of all natural numbers lying between 100 and 1000, which are
multiples of 5.\\
\solution
\input{ncert-maths/11/9/2/2/2.tex}
\pagebreak

\item Find the sum of odd numbers between 0 and 50.\\
\solution
\input{}
\pagebreak

\item  A ladder has rungs 25cm apart.The rungs decrease uniformly in length from 45cm at the bottom to 25cm at the top.If the top and bottom rungs are 2 and 1/2 meter apart.what is length of wood required for the rungs?\\
\pagebreak

\item Q2) The sum of the third and the seventh terms of AP is 6 and their product is 8. Find the sum of first sixteen terms of the AP \\
\solution
\pagebreak
\item A spiral is made up of successive semicircles, with centres alternately at A and B, starting with centre at A, of radii $0.5 cm$, $1.0 cm$, $1.5 cm$, $2.0 cm$, . . . What is the total length of such a spiral made up of thirteen consecutive semicircles? (Take $\pi = \frac{22}{7}$)\\
\solution
\newpage
\item In an A.P., if the $p$-th term is $\frac{1}{q}$ and $q$-th term is $\frac{1}{p}$, prove that the sum of the first $pq$ terms is $\frac{1}{2}\brak{pq + 1}$, where $p \neq q$.
\solution
\pagebreak

\item Find the sum to indicated number of terms in each of the geometric progressions in
$0.15, 0.015, 0.0015\ldots 20 terms$.\\
\solution
\input{ncert-maths/11/9/3/7/assignment2.tex}
\pagebreak

\item A contract on construction job specifies a penalty for delay of completion beyond a certain date as follows: \rupee $200$ for the first day, \rupee $250$ for the second day, \rupee $300$ for the third day, etc., the penalty for each succeeding day being \rupee $50$ more than for the preceding day.How much money the contractor has to pay as penalty, if he has delayed the work by $30$ days?\\
\solution
\pagebreak

\item A man deposited Rs 10000 in a bank at the rate of 5\% simple interest anually. Find the amount in 15\textsuperscript{th} year since he deposited the amount and also calculate the total amount after 20 years.\\
\solution
\input{ncert-maths/11/9/5/30/main.tex}
\pagebreak

\end{enumerate}
