\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
\item The $4^{th}$ term of a G.P. is square of its second term, and the first term is -3. Determine its $7^{th}$ term.\\  

\solution 

\input{ncert-maths/11/9/3/4/discrete1.tex}
\pagebreak

\item Show that
\begin{equation}
    \frac{1\times2^2 + 2\times3^2 + \dots + n\times\brak{n+1}^2}{1^2\times2 + 2^2\times3 +\dots + n^2\times\brak{n+1}}  = \frac{3n+5}{3n+1}\notag
\end{equation}

\solution 

\input{ncert-maths/11/9/5/26/main.tex}
\pagebreak

\item Write the five terms at n = 1, 2, 3, 4, 5 of the sequence and obtain the Z-transform of the series
\begin{align}
    x \brak{n} &=  -1, & n = 0 \\
    &=   \frac{x \brak{n-1}}{n}, & n > 0\\
    &=   0, & n < 0 
\end{align}

\solution

\input{ncert-maths/11/9/1/12/main.tex}
\pagebreak


\item Subba Rao started work in 1995 at an annual salary of Rs. 5000 and received an increment of Rs. 200 each year. In which year did his income reach Rs. 7000?

\solution

\input{ncert-maths/10/5/2/19/main.tex}

\item Consider the sequence whose $n^\text{th}$ term is given by \(2^n\). Find the first 6 terms of this sequence.

\solution

\input{ncert-maths/11/9/1/3/2.tex}

\item If the sum of first 7 terms of an AP is 49 and that of 17 terms is 289, find the sum of first n terms.

\solution

\input{ncert-maths/10/5/3/9/main.tex}
\pagebreak

\item Write the first five terms of the sequence and obtain the corresponding series:\\
$a_1=a_2=2,$ $a_n=a_{n-1} -1,$ $n>2$\\
\solution
\input{ncert-maths/11/9/1/13/main.tex}
\pagebreak
\item Insert two numbers between 3 and 81 so that the resulting sequence is G.P.\\

\solution
\input{ncert-maths/11/9/3/26/asnmt1.tex}
\pagebreak

\item  What will Rs 500 amounts to in 10 years after its deposit in a bank which pays annual interest rate of 10$\%$ compounded annually?

\solution
    \input{ncert-maths/11/9/3/31/main.tex}
\pagebreak

\item Find the $20^{th}$ term from the last term of the AP: $3,8,13.....253$.

\solution
\input{ncert-maths/10/5/2/17/main.tex}

\pagebreak
\item Find the sum to $n$ terms of series , whose $n^{th}$ term is : $n(n+1)(n+4)$.

\solution
\input{ncert-maths/11/9/4/8/math.11.9.4.8.tex}
\pagebreak

\item Find the indicated terms in the sequence whose nth terms is $a(n)$ = $4n-3$. Find $a(17)$ and $a(24)$.
    
\solution 
\input{ncert-maths/11/9/1/7/7.tex}
\pagebreak

\item The difference between any two cosecutive interior angles of a polygon is $5^\circ$.If the smallest angle is $120^\circ$,find the number of sides of polygon. \\
\solution
\input{ncert-maths/11/9/2/18/ass_1.tex}
\pagebreak
\item The $5$th,$8$th and $11$th terms of a GP are p,q and s respectively .show that $q^2=ps$ \\
\solution
\input{ncert-maths/11/9/3/3/assign1.tex}
\pagebreak
\item The sum of the first four terms of an A.P. is 56. The sum of the last four terms is
 112. If its first term is 11, then find the number of terms.\\
\solution
\input{ncert-maths/11/9/5/12/Assignment2.tex}
\pagebreak
\item Find the sum to $n$ terms of the series whose $n^{th}$ term is given by $(2n-1)^2$ ? 
\solution
\pagebreak
\item If the $4^{th}$, $10^{th}$ and $16^{th}$ terms of a G.P. are $x$, $y$, and $z$, respectively. Prove that $x,\; y,\; z$ are in G.P. \\
\solution
\input{ncert-maths/11/9/3/17/A_1.tex}
\pagebreak
\item Show that the ratio of the sum of the first \(n\) terms of a geometric progression (G.P.) to the sum of terms from \((n+1)\)th to \((2n)\)th term is \(\frac{1}{r^n}\).
\solution
\pagebreak
\item A G.P consists of an even number of terms. If the sum of all terms is 5 times the sum of terms occupying odd places, then find its common ratio.\\
\solution
\input{ncert-maths/11/9/5/11/firstcorrection.tex}
\pagebreak
\item Find the sum to indicated number of terms in the geometric progression $x^3,x^5,x^7,...n$ terms (if $x\neq\pm1$).\\
\solution
\input{ncert-maths/11/9/3/10/11.9.3.Q10.tex}
\pagebreak
\item Determine the AP whose third term is 16 and the 7th term exceeds the 5th term by 12. \\
\solution
\input{ncert-maths/10/5/2/16/1.tex}
\pagebreak
\item Find the seventh term of the sequence where the nth term is given by $a_n= \frac {n^2}{2^{n}}$\\
\solution
\input{ncert-maths/11/9/1/8/a1.tex}
\pagebreak
\item Find sum to n terms of the following series:\\
$\frac{1}{1 \times 2} + \frac{1}{2 \times 3} + \frac{1}{3 \times 4} + \ldots$ \hfill(NCERT 11.9.4.4)
\solution
\pagebreak
\item 1x2x3 + 2x3x4 + 3x4x5 +..... \\
\solution
\pagebreak
\item  Find the sum of the following series up to \(n\) terms:
          \begin{enumerate}
              \item $5 + 55 + 555 + \ldots$
              \item  $.6 + .66 + .666 + \ldots$
        \end{enumerate}

\solution
\pagebreak
\item Find $a_{9}$ in the sequence $a_{n}=\brak{-1}^{n-1}n^{3}$ \\
\solution
\pagebreak
\item Find the 20th term in this series.\\
$$2\times4+4\times6+6\times8\cdots+n\,terms$$ \\
\solution
\pagebreak

\item Q10) The sum of three numbers in G.P. is 56. If we subtract 1, 7, 21 from these numbers in that order, we obtain an arithmetic progression. Find the numbers.\\
\solution
\item  Find the sum to n terms for the given series: $3\times8 + 6\times11 + 9\times14 + ...$
\solution
\pagebreak
\item Find the sum to $n$ terms of the series:\\
$1^2+\brak{1^2+2^2}+\brak{1^2+2^2+3^2}+...$ \hfill(NCERT 11.9.4.7)\\
\solution
\pagebreak
\item Find a GP for which sum of the first two terms is -4 and the fifth term is 4 times the third term.\\
\solution
\input{ncert-maths/11/9/3/16/question2.tex}
\pagebreak

\item Find the sum of the following series up to n terms and obtain the Z-transform: 
$$\ldots + 0 + \frac{1^3}{1} + \frac{1^3 + 2^3}{1 + 3} + \frac{1^3 + 2^3 + 3^3}{1 + 3 + 5} + \ldots$$
\solution
\pagebreak
\item  If the first and the  $n^{th}$  term of a G.P. are $a$ and $b$, respectively, and if $P$ is the product of $n$ terms , prove that $ P^2 = \brak{ab}^n $ \hfill(NCERT 11.9.3.22)\\
\solution
\pagebreak
\end{enumerate}
